\section{Summary}
In this thesis we have investigated the possibility of using \textit{reUpNix} as the
host \ac{OS} for running the popular \textit{Azure IoT} platform on \ac{IIoT} devices.
We have focused on the update mechanism of \textit{reUpNix} and how it can be used
to save bandwidth when updating the \ac{OS} and \ac{OCI}-container images on the device,
since some \ac{IoT} devices have limited bandwidth because they are installed in
remote locations and/or have limited storage. We were able to show that \textit{Azure IoT Edge}
can be packaged and run on the \textit{Nix}-based \textit{reUpNix} and
\textit{reUpNix}'s \textit{Nix store} does not introduce any significant overhead
or delay when recovering from a reboot. When comparing \textit{reUpNix} to
other \ac{OS} that are able to run \textit{Azure IoT Edge}, we observed that \textit{reUpNix}
had a significantly smaller image size than the other \ac{OS}. In particular,
\textit{reUpNix} has a 43\% smaller image size than for example Microsoft's
recommended \textit{Ubuntu 22.04}. We also showed that \textit{reUpNix}'s update
methodology is significantly more efficient than the commonly used A/B partition
schema. In our tests, \textit{reUpNix} was able to update the \ac{OS} and save
90.3\% of the transferred data compared to a A/B partition schema with \textit{Ubuntu 22.04}.


\section{Conclusion}
It was shown that reUpNix has the the potential to drastically reduce the transferred
data when updating the operating system, which is important for \ac{IIoT} devices
that have a limited Internet connection. \textit{reUpNix} provides a viable
alternative for \ac{IoT} devices running \textit{Azure IoT Edge}
to the commonly used A/B partition schema, which is used by most platforms,
including the \textit{Azure Device Update Service}.

However, Microsoft does not officially support NixOS or reUpNix, which may be a decisive factor
for product managers choosing an \ac{OS} for their \ac{IIoT} devices. Microsoft
only provides so called "Tier 1" support for Ubuntu, Debian, Red Hat Enterprise
Linux and Windows, which means that Microsoft is actively testing and validating
new releases. If a developer is using an \ac{OS} that is not officially supported
and encounters a problem, they need to reproduce the issue with one of Microsoft's
"Tier 1" supported \ac{OS} before they can open a support ticket with Microsoft
\cite{msdoc-supportetplatforms}.

Lastly, \textit{reUpNix}'s differential updates also reduce the data transmitted
when updating or installing \ac{OCI}-container images, compared to using \code{docker pull}.
This is important for \ac{IIoT} devices that run \textit{Azure IoT Edge} or other
container runtimes, which enables them to update their container images more frequently
and bring customers new features faster in an edge computing environment.


\section{Future Work}
In order to store the \ac{OCI}-container images in the \textit{Nix store} and
handle the update of the images easier, we could implement a custom storage
provider for docker images that uses the \textit{Nix store} as the backend.
This would eliminate some of the complexity of the current solution and reduce
the overhead required to load the container images.

Further, we could investigate the possibility of implementing a custom update
handler for the \textit{Azure Device Update Agent} since Microsoft allows
the implementation of custom update handlers. This would allow us replace the
currently script handler with a dedicated update handler that is compatible
with \textit{reUpNix}'s update mechanism and has lower overhead.

Lastly, we have not shown that the system we have built is the smallest possible
system to run \textit{Azure IoT Edge} on. There are still possibilities to explore, which
further minify the system, such as using \textit{Podmand} instead of \textit{Docker}
or minifying the \textit{Azure IoT Edge} runtime and the \textit{Azure IoT Edge} modules
or using software like \textit{upx} to compress binaries.
